The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-05-04 exp-resurgence.tex
Revise motivation
Drop old text from countable cover and Bessel 0

@@

For any $\mu \in \C \smallsetminus \Z$, the classical modified Bessel function $K_\mu(z)$ can be expressed as the thimble integral
\begin{equation}\label{int:mod-bessel-gen}
 K_\mu(z) = \frac{1}{2 \sinh(\mu i\pi)} \int_{\mathcal{C}^\theta_1} \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt
\end{equation}
for $|\theta| < \tfrac{\pi}{2}$. This formula can be deduced, with a lot of finagling, from formulas 10.32(ii) and 10.27.4 of \cite{dlmf}\begin{todo}{[Cite Watson too?]}\end{todo}.
\begin{verify}
\par
From equation~6.22(3) of Watson's \textit{A treatise on the theory of Bessel functions} (1944), p. 181 (the reference in \cite{dlmf}):
\begin{align*}
2\pi i \, I_\mu(z) &= \int_{+\infty}^0 e^{z\cosh(-\pi i+a)-\mu(-i\pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)}\,da +\int_{-\pi}^{\pi} e^{z\cosh(ib)-\mu i b}\,db\\
& = -\int_{-\infty}^0 e^{z\cosh(-\pi i-a)+\mu(i \pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i \pi  +a)}\,da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b)\,db\\
& = -\int_{-\infty}^0 e^{z\cosh(\pi i+a)+\mu(i\pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)}\,da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b)\,db.
\end{align*}
Hence,
\begin{align*}
4 i \sin(\mu \pi) K_\mu(z) & = 2\pi i \big[ I_{-\mu}(z) - I_\mu(z) \big] \\
& = \int_{-\infty}^0 e^{z\cosh(\pi i+a)}\left[-e^{-\mu(i\pi +a)}+e^{\mu(i\pi +a)}\right]\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)}\left[e^{\mu(i\pi +a)}-e^{-\mu(i\pi +a)}\right]\,da \\
& \textcolor{OrangeRed}{= 2\int_{-\infty}^0 e^{z\cosh(\pi i+a)} \sinh\big(\mu(a+i\pi)\big)\,da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh(\mu(i\pi+a)\big)\,da} \\
& = 2\int_{-\infty}^0 e^{z\cosh(-\pi i+a)} \sinh\big(\mu(a-i\pi)\big)\,da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh\big(\mu(i\pi+a)\big)\,da
\end{align*}
\color{OrangeRed}
Stop at the highlighted line! This simplifies to the integral
\[ 2 \int_\gamma e^{z\cosh(t)} \sinh(\mu t)\,dt \]
along the contour $\gamma$ that runs rightward along $i\pi + \R$. \textcolor{magenta}{The integral on the next line is {\em not} the path coming from infinity along $(-\infty,0) + 2\pi i (j - \tfrac{1}{2})$ and returning to infinity along $(0, \infty) + 2\pi i (j + \tfrac{1}{2})$, because it skips the segment along $i(-\pi, \pi)$.}
\par
\end{verify}
The integral converges when $z$ is in the right half-plane. Choosing a rational parameter $\mu = \tfrac{m}{n}$ gives formula~\eqref{integral:mod-bessel-lifted}, showing that $K^{(j)}_{m/n}(z)$ is the classical modified Bessel function $K_{m/n}(z)$ when $j$ is odd.

@@

To confirm that the calculation above is consistent with Section~\ref{countable-cover}, recall formula~\eqref{eq: K_j_mu at 1}:
\[ K_0^{(1)}(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta. \]
The hypergeometric function in the integrand can be expressed algebraically using identity~15.4.13 from \cite{dlmf}. This leads to an expression for the integrand that makes its $\zeta_{\pm 1}^{1/2}$ singularities even more apparent:
\begin{equation}\label{eqn:borel_bessel0}
K_0^{(1)}(z) = \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\big(\zeta^2 - 1\big)^{-1/2}\;d\zeta.
\end{equation}
We could get the same result from formula~\eqref{int:k0_cosh} by trigonometric substitution. This is a special case of formula~10.32.8 from \cite{dlmf}.

\color{RoyalBlue}
When $\mu$ goes to $0$, formula~\eqref{int:mod-bessel-gen} becomes
\[ K_0^{(j)}(z) = \frac{1}{2\pi i} \int_ {\mathcal{C}_j^\theta} \exp\left[z \cosh(t)\right]\,t\,dt. \]
We will evaluate
\[ K_0(z) \defeq K_0^{(1)}(z) - K_0^{(0)}(z). \]
In this difference, the parts of $\mathcal{C}_1^\theta$ and $\mathcal{C}_0^\theta$ in the left half-plane cancel out \textcolor{orange}{[$\theta$ is small]}, leaving the integral
\[ K_0(z) = \frac{1}{2\pi i} \int_\mathscr{c} \exp\left[z \cosh(t)\right]\,t\,dt \]
over the contour $\mathscr{c}$ that runs as follows:
\begin{enumerate}
\item Leftward along $(0, \infty) + (-\pi + \theta)i$.
\item Upward along $(-\pi + \theta, \pi + \theta)i$.
\item Rightward along $(0, \infty) + (\pi + \theta)i$.
\end{enumerate}
Since the integrand is an odd function, the upward part of the path integrates to zero. Since the integrand is also $2\pi i$-periodic, the leftward and rightward parts of the integral collapse to
\begin{align}
K_0(z) & = \frac{1}{2\pi i} \int_{\mathcal{J}^0_{t, 0}} \exp\left[z \cosh(t + \pi i)\right]\,\pi i\,dt \notag - \frac{1}{2\pi i} \int_{\mathcal{J}^0_{t, 0}} \exp\left[z \cosh(t - \pi i)\right]\,\pi i\,dt \notag \\
& = \frac{1}{2\pi i} \int_{\mathcal{J}^0_{t, 0}} \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \notag \\
& = \int_{\mathcal{J}^0_{t, 0}} \exp\left[-z \cosh(t)\right]\,dt \label{int:k0_cosh_old} \\
& = \int_{\mathcal{J}^0_{s, 1}} \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s}, \notag
\end{align}
with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}.

To confirm that the calculation above is consistent with Section~\ref{countable-cover}, use formulas \eqref{eq: K_j_mu at 1} and \eqref{eq: K_j_mu at -1} to get
K_0(z) & = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
& \hphantom{=} - \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta
The hypergeometric function in the integrand can be simplified away using identity~15.4.13 from \cite{dlmf}, leaving an expression that makes the $\zeta_{\pm 1}^{1/2}$ singularities of the integrand even more apparent: \textcolor{magenta}{[result is right, but reasoning is wrong: integrals can't be directly combined, because they use different contours]}
\begin{equation}\label{eqn:borel_bessel0}
K_0(z) = \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\big(\zeta^2 - 1\big)^{-1/2}\;d\zeta.
We could get the same result from equation~\eqref{int:k0_cosh} by trigonometric substitution. This is a special case of formula~10.32.8 from \cite{dlmf}.
\par
For odd $j$, with $-\eta^2 = \tfrac{1}{2} - \tfrac{\zeta}{2}$, equation~\eqref{eq: K_j_mu at 1} gives \textcolor{GreenYellow}{(we were missing a factor of two in identity~15.4.13, so the highlighted factors of $1/2$ should be removed)}
K^{(j)}_0(z) & = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
& = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \textcolor{GreenYellow}{\frac{1}{2}} (1 + \eta^2)^{-1/2} \\
& = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \textcolor{GreenYellow}{\frac{1}{2}} \left(\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \\
& = -\frac{1}{2} \textcolor{GreenYellow}{\frac{1}{2}} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} d\zeta \\
& = -\textcolor{GreenYellow}{\frac{1}{2}} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
This is off by a sign from what we expect, but the sign could be accounted for by the branch cuts in the square roots. For even $j$, with $-\eta^2 = \tfrac{1}{2} + \tfrac{\zeta}{2}$, equation~\eqref{eq: K_j_mu at -1} gives
K^{(j)}_0(z) & = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta \\
& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \textcolor{GreenYellow}{\frac{1}{2}} (1 + \eta^2)^{-1/2} d\zeta \\
& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \textcolor{GreenYellow}{\frac{1}{2}} \left(\frac{1}{2} - \frac{\zeta}{2}\right)^{-1/2} d\zeta \\
& = \color{DarkViolet}\textcolor{GreenYellow}{\frac{1}{2}} \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left[\left(-\frac{1}{2}-\frac{\zeta}{2}\right)  \left(\frac{1}{2} - \frac{\zeta}{2}\right)\right]^{-1/2} d\zeta  \\
& =  \color{DarkViolet} \textcolor{GreenYellow}{\frac{1}{2}} \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{4}+\frac{\zeta^2}{4}\right)^{-1/2} d\zeta  \\
& = \color{DarkViolet} \textcolor{GreenYellow}{\frac{1}{2}} 3 \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta \\
& = \color{DarkViolet} -\textcolor{GreenYellow}{\frac{1}{2}} 3 \int_{\mathcal{J}^{\theta+\pi}_{\zeta, 1}} e^{z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
%%& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \textcolor{Tomato}{i} \left(\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{\textcolor{Tomato}{i}}{2} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \textcolor{Tomato}{\quad\text{(is this justified?)}} \\
%%& = \textcolor{Tomato}{-}\frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} d\zeta \\
%%& = \textcolor{Tomato}{-}\frac{2 \cdot 3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
$\int_{-1}^{e^{i\theta}\infty} = \int_{-1}^{e^{-i\theta}\infty}+2 \int_{1}^{\infty}$

We can also verify equation \eqref{eqn:borel_bessel0} using the thimble projection formula, \eqref{eqn:formula-proof}. From the expression of $K_0$ 
\begin{equation}
K_0(z)=\int_0^{\infty} \exp(-z\cosh(t)) dt,
\end{equation}
we set $\zeta=\cosh(t)$. Choosing a branch for the square root
\begin{align*}
d\zeta & = \sinh(t) dt\\
& =  \sqrt{\zeta^2-1} \, dt
\end{align*}
we finally get 
\[\int_{\mathcal{J}^0_{\zeta, 1}} e^{-z\zeta} \frac{d\zeta}{\sqrt{\zeta^2-1}}\]
\end{verify}
\color{black}
%
\subsection{Generalized Airy}
%
In \cite{Reid} and the appendix of \cite{drazin-reid}, Drazin and Reid construct approximate solutions of the Orr--Sommerfield fluid equation using the generalized Airy functions
\begin{align*}
\mathrm{A}_k(y,p) & = \frac{1}{2\pi i}\int_{\mathscr{a}_k} \exp\big[yt-\tfrac{t^3}{3}\big]\,\frac{dt}{t^p} & & p \in \C\hphantom{{}_{\le 0}},\quad k \in \{1,2,3\} \\
\mathrm{B}_0(y,p) & = \frac{1}{2\pi i}\int_{\mathscr{b}_0} \exp\big[yt-\tfrac{t^3}{3}\big]\,\frac{dt}{t^p} & & p \in \Z \\
\mathrm{B}_k(y,p) & = \hphantom{\frac{1}{2\pi i}} \int_{\mathscr{b}_k} \exp\big[yt-\tfrac{t^3}{3}\big]\,\frac{dt}{t^p}, & & p \in \Z_{\le 0},\quad k \in \{1,2,3\}
\end{align*}
which are defined by integrals along the contours $\mathscr{a}_k, \mathscr{b}_0, \mathscr{b}_k$ shown in Figure~\ref{fig:path-generalized-Airy}~\cite{drazin-reid}\cite[Section 9.13(ii)]{dlmf}.
\begin{figure}[ht]
\center
\newcommand{\apathcolor}{ietcoast}
\newcommand{\bpathcolor}{black}
\begin{tikzpicture}
\renewcommand{\dotsize}{0.08}
\fill[pwbeige!10] circle(3.95);
\begin{scope}[\bpathcolor, very thick, -stealth]
  \draw (80:0.8) arc (80:400:0.8);
  \node at (60:0.8) {$\mathscr{b}_0$};
  \foreach \ang/\name in {0/1, 120/2, 240/3} {
    \draw[very thick,-stealth] (0, 0) -- ++(\ang:4) node[anchor=\ang-180] {$\mathscr{b}_\name$};
  };
  \fill (1.25, 0) circle (\dotsize) node[anchor=north west] {$\tfrac{1}{2}$};
  \draw[fill=white, thin] circle (\dotsize);
\end{scope}
\begin{scope}[\apathcolor, very thick, -stealth]
  \foreach \ang/\name in {0/1, 120/2, 240/3} {
    \draw[rotate=\ang] (-0.5, 0) +(-120:3.75) .. controls +(62:1) and +(0, -1.2) .. +(-0.75, 0) .. controls +(0, 1.2) and +(-62:1) .. +(120:3.75) node[midway, anchor=\ang+30] {$\mathscr{a}_\name$};
  };
  \fill (-1.25, 0) circle (\dotsize) node[anchor=north east] {$-\tfrac{1}{2}$};
\end{scope}
\end{tikzpicture}
\caption{The integration contours in the $t$ plane that define $\mathrm{A}_k,\mathrm{B}_0,\mathrm{B}_k$.}\label{fig:path-generalized-Airy}
\end{figure}
These functions satisfy the generalized Airy equation
\[ \left[\big(\tfrac{\partial}{\partial y}\big)^3 - y\,\tfrac{\partial}{\partial y} + (p-1)\right] \Phi = 0. \]
When $p = 0$, this equation reduces to
\[ \tfrac{\partial}{\partial y} \circ \left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \Phi = 0, \]
which is equivalent to an inhomogeneous version of the classical Airy equation.

>>>>

\item For a kernel $k$ on $B \times B$, we the corresponding integral kernel operator would be
\[ \mathcal{V}\phi = \int_0^\zeta k\,\phi'\,d\zeta' \]
If we have, for example, $k = (\zeta - \zeta')^\rho$ and $\phi' = (\zeta')^k$, then
\[ \mathcal{V}\phi = \int_0^\zeta (\zeta - \zeta')^\rho\,(\zeta')^k\,d\zeta' \]
\item Suppose you have
\[ \omega = e^\zeta - 1 = \zeta + \tfrac{1}{2!} \zeta^2 + \tfrac{1}{3!} \zeta^3 + \ldots \]
Then
\[ \zeta = \log(1 + \omega) = \omega + \tfrac{1}{2} \omega^2 + \tfrac{1}{3} \omega^3 + \ldots \]
Do you say $\zeta(\omega)$? Or $\omega(\zeta)$? What does $\omega(\zeta + 1)$ mean? Define $f = \zeta + \omega$. What is $f(\omega + 1)$? $f(\zeta) = \zeta + \omega(\zeta)$. So $f(\omega) = \log(1 + \omega) + \omega$, so $f(\zeta) = \zeta + e^\zeta - 1$?
\[ \int_0^\zeta (\zeta^2 + \zeta'^2)\,d\zeta' \]
\[ \int_{\zeta=0}^a (\zeta(a)^2 + \zeta^2)\,d\zeta \]
\[ \int_{\zeta=0}^a (\zeta^2 + \zeta^2)\,d\zeta \]

@@

For any $\mu \in \C \smallsetminus \Z$, the classical modified Bessel function $K_\mu(z)$ can be expressed as the thimble integral
\begin{equation}\label{int:mod-bessel-gen}
 K_\mu(z) = \frac{1}{2 \sinh(\mu i\pi)} \int_{\mathcal{C}^\theta_1} \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt
\end{equation}
for $|\theta| < \tfrac{\pi}{2}$. This formula can be deduced, with a lot of finagling, from formulas 10.32(ii) and 10.27.4 of \cite{dlmf}\begin{todo}{[Cite Watson too?]}\end{todo}.
\begin{verify}
\par
From equation~6.22(3) of Watson's \textit{A treatise on the theory of Bessel functions} (1944), p. 181 (the reference in \cite{dlmf}):
\begin{align*}
2\pi i \, I_\mu(z) &= \int_{+\infty}^0 e^{z\cosh(-\pi i+a)-\mu(-i\pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)}\,da +\int_{-\pi}^{\pi} e^{z\cosh(ib)-\mu i b}\,db\\
& = -\int_{-\infty}^0 e^{z\cosh(-\pi i-a)+\mu(i \pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i \pi  +a)}\,da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b)\,db\\
& = -\int_{-\infty}^0 e^{z\cosh(\pi i+a)+\mu(i\pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)}\,da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b)\,db.
\end{align*}
Hence,
\begin{align*}
4 i \sin(\mu \pi) K_\mu(z) & = 2\pi i \big[ I_{-\mu}(z) - I_\mu(z) \big] \\
& = \int_{-\infty}^0 e^{z\cosh(\pi i+a)}\left[-e^{-\mu(i\pi +a)}+e^{\mu(i\pi +a)}\right]\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)}\left[e^{\mu(i\pi +a)}-e^{-\mu(i\pi +a)}\right]\,da \\
& = 2\int_{-\infty}^0 e^{z\cosh(\pi i+a)} \sinh\big(\mu(a+i\pi)\big)\,da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh(\mu(i\pi+a)\big)\,da.
\end{align*}
This simplifies to the integral
\[ 2 \int_\gamma e^{z\cosh(t)} \sinh(\mu t)\,dt \]
along the contour $\gamma$ that runs rightward along $i\pi + \R$.
\par
\end{verify}
The integral converges when $z$ is in the right half-plane. Choosing a rational parameter $\mu = \tfrac{m}{n}$ gives formula~\eqref{integral:mod-bessel-lifted}, showing that $K^{(j)}_{m/n}(z)$ is the classical modified Bessel function $K_{m/n}(z)$ when $j$ is odd.

@@

To confirm that the calculation above is consistent with Section~\ref{countable-cover}, recall formula~\eqref{eq: K_j_mu at 1}:
\[ K_0^{(1)}(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta. \]
The hypergeometric function in the integrand can be expressed algebraically using identity~15.4.13 from \cite{dlmf}. This leads to an expression for the integrand that makes its $\zeta_{\pm 1}^{1/2}$ singularities even more apparent:
\begin{equation}\label{eqn:borel_bessel0}
K_0^{(1)}(z) = \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\big(\zeta^2 - 1\big)^{-1/2}\;d\zeta.
\end{equation}
We could get the same result from formula~\eqref{int:k0_cosh} by trigonometric substitution. This is a special case of formula~10.32.8 from \cite{dlmf}.
%
\subsection{Generalized Airy}
%
In \cite{Reid} and the appendix of \cite{drazin-reid}, Drazin and Reid construct approximate solutions of the Orr--Sommerfield fluid equation using the generalized Airy functions
\begin{align*}
\mathrm{A}_k(y,p) & = \frac{1}{2\pi i}\int_{\mathscr{a}_k} \exp\big[yt-\tfrac{t^3}{3}\big]\,\frac{dt}{t^p} & & p \in \C\hphantom{{}_{\le 0}},\quad k \in \{1,2,3\} \\
\mathrm{B}_0(y,p) & = \frac{1}{2\pi i}\int_{\mathscr{b}_0} \exp\big[yt-\tfrac{t^3}{3}\big]\,\frac{dt}{t^p} & & p \in \Z \\
\mathrm{B}_k(y,p) & = \hphantom{\frac{1}{2\pi i}} \int_{\mathscr{b}_k} \exp\big[yt-\tfrac{t^3}{3}\big]\,\frac{dt}{t^p}, & & p \in \Z_{\le 0},\quad k \in \{1,2,3\}
\end{align*}
which are defined by integrals along the contours $\mathscr{a}_k, \mathscr{b}_0, \mathscr{b}_k$ shown in Figure~\ref{fig:path-generalized-Airy}~\cite{drazin-reid}\cite[Section 9.13(ii)]{dlmf}.
\begin{figure}[ht]
\center
\newcommand{\apathcolor}{ietcoast}
\newcommand{\bpathcolor}{black}
\begin{tikzpicture}
\renewcommand{\dotsize}{0.08}
\fill[pwbeige!10] circle(3.95);
\begin{scope}[\bpathcolor, very thick, -stealth]
  \draw (80:0.8) arc (80:400:0.8);
  \node at (60:0.8) {$\mathscr{b}_0$};
  \foreach \ang/\name in {0/1, 120/2, 240/3} {
    \draw[very thick,-stealth] (0, 0) -- ++(\ang:4) node[anchor=\ang-180] {$\mathscr{b}_\name$};
  };
  \fill (1.25, 0) circle (\dotsize) node[anchor=north west] {$\tfrac{1}{2}$};
  \draw[fill=white, thin] circle (\dotsize);
\end{scope}
\begin{scope}[\apathcolor, very thick, -stealth]
  \foreach \ang/\name in {0/1, 120/2, 240/3} {
    \draw[rotate=\ang] (-0.5, 0) +(-120:3.75) .. controls +(62:1) and +(0, -1.2) .. +(-0.75, 0) .. controls +(0, 1.2) and +(-62:1) .. +(120:3.75) node[midway, anchor=\ang+30] {$\mathscr{a}_\name$};
  };
  \fill (-1.25, 0) circle (\dotsize) node[anchor=north east] {$-\tfrac{1}{2}$};
\end{scope}
\end{tikzpicture}
\caption{The integration contours in the $t$ plane that define $\mathrm{A}_k,\mathrm{B}_0,\mathrm{B}_k$.}\label{fig:path-generalized-Airy}
\end{figure}
These functions satisfy the generalized Airy equation
\[ \left[\big(\tfrac{\partial}{\partial y}\big)^3 - y\,\tfrac{\partial}{\partial y} + (p-1)\right] \Phi = 0. \]
When $p = 0$, this equation reduces to
\[ \tfrac{\partial}{\partial y} \circ \left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \Phi = 0, \]
which is equivalent to an inhomogeneous version of the classical Airy equation.
